---
title: "Data Analysis"
author: "Chandni"
date: last-modified
bibliography: references.bib
---

## Introduction

This page demonstrates interactive data visualization using ggplot2 and plotly. The approach follows best practices for reproducible research [@wickham2016; @xie2018].

## Setup

```{r}
#| label: setup
#| message: false
#| warning: false

library(ggplot2)
library(plotly)
library(dplyr)
```

## Interactive Scatter Plot

The following visualization explores the relationship between vehicle weight and fuel efficiency in the `mtcars` dataset.

```{r}
#| label: fig-scatter
#| fig-cap: "Interactive scatter plot showing the relationship between weight and MPG, colored by number of cylinders"
#| warning: false

p <- ggplot(mtcars, aes(x = wt, y = mpg, color = factor(cyl), 
                         text = paste("Car:", rownames(mtcars)))) +
  geom_point(size = 3, alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE, linetype = "dashed") +
  scale_color_brewer(palette = "Set1") +
  labs(
    x = "Weight (1000 lbs)",
    y = "Miles per Gallon",
    color = "Cylinders"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom")

ggplotly(p, tooltip = c("text", "x", "y"))
```

As shown in @fig-scatter, there is a clear negative relationship between vehicle weight and fuel efficiency. Vehicles with more cylinders tend to be heavier and less fuel-efficient.

## Distribution Analysis

```{r}
#| label: fig-histogram
#| fig-cap: "Distribution of MPG values across all vehicles"
#| warning: false

p2 <- ggplot(mtcars, aes(x = mpg, fill = factor(cyl))) +
  geom_histogram(binwidth = 2, alpha = 0.7, position = "identity") +
  scale_fill_brewer(palette = "Set2") +
  labs(
    x = "Miles per Gallon",
    y = "Count",
    fill = "Cylinders"
  ) +
  theme_minimal()

ggplotly(p2)
```

## Box Plot Comparison

```{r}
#| label: fig-boxplot
#| fig-cap: "Comparison of MPG across different cylinder counts"
#| warning: false

p3 <- ggplot(mtcars, aes(x = factor(cyl), y = mpg, fill = factor(cyl))) +
  geom_boxplot(alpha = 0.7) +
  geom_jitter(width = 0.2, alpha = 0.5) +
  scale_fill_brewer(palette = "Pastel1") +
  labs(
    x = "Number of Cylinders",
    y = "Miles per Gallon",
    fill = "Cylinders"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

ggplotly(p3)
```

## Summary Statistics

```{r}
#| label: tbl-summary
#| tbl-cap: "Summary statistics by cylinder count"

mtcars %>%
  group_by(Cylinders = cyl) %>%
  summarise(
    `Mean MPG` = round(mean(mpg), 2),
    `SD MPG` = round(sd(mpg), 2),
    `Mean Weight` = round(mean(wt), 2),
    `N` = n()
  ) %>%
  knitr::kable()
```

## Methods {#sec-methods}

The analysis was conducted using R [@rcoreteam2023] with the following packages:

- **ggplot2** for static visualizations [@wickham2016]
- **plotly** for interactive features
- **dplyr** for data manipulation

## Conclusions

This exploratory analysis reveals several key patterns:

1. **Weight-efficiency trade-off**: Heavier vehicles consistently show lower fuel efficiency
2. **Cylinder effect**: More cylinders correlate with both higher weight and lower MPG
3. **Variation**: 4-cylinder vehicles show the highest variation in fuel efficiency

::: {.callout-tip}
## Reproducibility
All code in this analysis is fully reproducible. Download the source files from the [Data & Code](data.qmd) page.
:::

## References

::: {#refs}
:::
