---
title: "Data & Code"
---

## Overview

This page provides all materials needed to reproduce the analyses on this site. All data and code are freely available for download.

## Datasets

| Dataset | Description | Format | Download |
|---------|-------------|--------|----------|
| mtcars | Motor Trend Car Road Tests | CSV | [Download](data/mtcars.csv) |
| Example data | Demonstration dataset | CSV | [Download](data/example_data.csv) |

## R Scripts

| Script | Description | Download |
|--------|-------------|----------|
| analysis.R | Main analysis script | [Download](scripts/analysis.R) |
| figures.R | Figure generation | [Download](scripts/figures.R) |
| utils.R | Helper functions | [Download](scripts/utils.R) |

## Reproducibility Information

### R Session Info

```{r}
#| label: session-info
#| echo: false

sessionInfo()
```

### Package Versions

```{r}
#| label: pkg-versions
#| echo: false
#| message: false

pkgs <- c("ggplot2", "plotly", "dplyr", "knitr")
installed <- sapply(pkgs, function(x) {
  if (requireNamespace(x, quietly = TRUE)) {
    as.character(packageVersion(x))
  } else {
    "Not installed"
  }
})

data.frame(
  Package = pkgs,
  Version = installed
) |> knitr::kable()
```

## How to Reproduce

### Option 1: Clone the Repository

```bash
git clone https://github.com/chandniverse/chandniverse.github.io.git
cd chandniverse.github.io
```

Then open `chandniverse.github.io.Rproj` in RStudio.

### Option 2: Download Individual Files

Download the specific scripts and data files you need from the tables above.

### Option 3: Run in R

```r
# Install required packages
install.packages(c("ggplot2", "plotly", "dplyr", "knitr"))

# Source the analysis script
source("scripts/analysis.R")
```

## License

All code is released under the [MIT License](https://opensource.org/licenses/MIT). Data sources are cited in the respective analysis pages.

::: {.callout-note}
## Questions?
If you have trouble reproducing any analysis, please [open an issue](https://github.com/chandniverse/chandniverse.github.io/issues) on GitHub.
:::
